Examination of shapes! (homework exam)

### 2016-02-28 geometricAlgorithms/homeworkExam/homeworkExam.tex
to proof, also excersize 4 better

Now if you make the rectangle bigger something funny happens:

@@

In case we can do a perfect cut, do that.
If we can't do a perfect cut we have to minimize the largest area,
so start

\subsection{Vertex types}
Merge and split by definition, but on occasion a regular may happen to.
\section{Diagonal polygon cut}
The most obvious solution is the brute force solution, which involves
having two loops that compare every possible cut from every vertex.
and just keep track of the best cut. this will take $O(n^2)$ time.
\end{document}

>>>>

Now if you make the rectangle bigger something happens:

@@

\paragraph{To proof} Given a simple polygon $P$, the best horizontal cut
has at least one endpoint on a vertex of $P$, or it cuts $P$ into two pieces
with equal area (or both).

\paragraph{Proof} There are two cases to be proven:
	In case we can best horizontal cut a polygon $P$ into two equal areas
	we're done (since in this case there are no restrictions on the best
	horizontal cut line).
	In case we can't best horizontal cut polygon $P$ into two equal areas,
	the best horizontal cut has to minimise the larger area. In this case
	the best horizontal cut has to end on a vertex of $P$ according to
	the lemma. To prove this lets assume its not the case we end up of a
	vertex of $P$.
	However because the best horizontal cut has to minimize the larger
	area it will always end up on some sort of angle of the polygon, which
	is defined by a vertex and it can't equally divide the polygon because
	that was already handled
	by case one. So this shows that you end up with a contradiction.
	This is what had to be shown.

\subsection{Vertex types}
Merge and split by definition, but on occasion a regular may happen to.
\section{Diagonal polygon cut}
The most obvious solution is the brute force solution, which involves
having two loops that compare every possible cut from every vertex,
while keeping track of the best cut. This will take $O(n^2)$ time.

A faster method is just finding all the merge and split vertexes. Which takes
$O(n)$ time, and then comparing each of these with all other vertexes and keeping
track of the best area. This will take at most $O(n+(m+s)n)$
with $m$ as merge vertexes and $s$ as split vertexes. This is correct because in
exercise 3.b we determined that the vertexes a best horizontal cut intersects
with either a merge or split vertex, so the best diagonal cut will to.
\end{document}
